---
title: "Biostats uOttawa"
---

{{< include _links.qmd >}}

```{r}
#| label: setup
#| include: FALSE
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
#| fig.align: 'center'
#| out.width: "25%"
dat<-data.frame(a = rnorm(10000))
library(ggplot2)
ggplot(dat, aes(a))+geom_density(color="blue", fill="red") +theme_classic()+xlab("Gaussian distribution")
```

::: {.panel-tabset }


## English

### Biostatistic courses at uOttawa

This regroup the different resources developed for the biostatistic courses at the university of Ottawa
by [Julien Martin](people.qmd)  

#### Applied biostatistics with R (BIO 4X58):

  * Offered to both undergraduate and graduate students in english and french
  * Prerequisite:
    * an introduction class to statisticis is good to have
    * No (or limited) knowledge of R and no (or limited) knowledge of stats expected.
  * BIO4158 english ([Course site][4158_course] / [Course manual][4158_manual])
  * BIO4558 french ([Course site][4558_course] / [Course manual][4558_manual])

#### Advanced biostatistics and open science (BIO 8940)

  * Bilingual course for graduate students
  * Prerequisite:
    * a functional knowledge of R (loading data, running basic linear models, and making plots) 
    * a good understanding of linear models
    * essentially Bio8940 is a great next steps after completing Bio4x58.
  * [Course site][8940_course] / [Course manual][8940_manual]

### Extra resources

* An introduction to R
  * english ([course][Rintro] / [course manual][R_way])
  * french ([course][introR] / [course manual][chemin_R])

### Statistical consulting {#consult}

As Part of my service in the Biology department, I provide statistical consulting.
Please just contact me to book an appointment to discuss your stat problems.

Please bring with you (or send me in advance):

* your data
* your R code (should at least load the data into R)
* a clear working hypothesis

Statistical consulting does not mean that you have to add me as a co-author. I just ask that you add me to the **"Acknowledgements"** of your thesis and manuscript/article. Repeated consulting on the same problem and my implication on developing project specific coding/analysis might lead to co-authorship, but this usually all comes naturally and is always discussed openly with the student(s) and PI(s). As yet, I have never requested to become a co-author and I was offered co-authorship for 3 manuscripts over > 50 projects discussed.

## Français

### Cours de biostatistique à uOttawa

Le site regroupe les différentes ressources développées par [Julien Martin](people.qmd) pour les cours de biostatistiques à uOttawa

#### Biostatistiques appliquées avec R (BIO 4X58)

  * Cours offerts aux étudiant au baccaulauréat et aux étudiants gradués en anglais et en français
  * Pré-requis:
    * cours d'introduction au statistiques recommandée
    * Aucune connaissance de R et des statistiques requises
  * BIO4158 anglais ([cours][4158_course] / [manuel][4158_manual])
  * BIO4558 français ([cours][4558_course] / [manuel][4558_manual])

#### Biostatistiques avancées et science ouverte (BIO8940)

  * Cours bilingues offerts aux étudiants gradués
  * Pré-requis:
    * connaissances fonctionelle de R (chargement de données, graphique et statistiques de bases)
    * bonne compréhension des modèles linéaires
    * Essentiellement Bio4x58
  * [cours][8940_course] / [manuel][8940_manual]

### Tutoriels

* Introduction à R
  * anglais ([cours][Rintro] / [manuel][R_way])
  * français ([cours][introR] / [manuel][chemin_R])

### Consultations en statistique

Je fournis des services de consultation en biostatistique dans le cadre de mon service au département de Biologie.
Pour discuter de vos problèmes en statistiques, veuillez simplement me contacter pour prendre un rendez-vous.

Veuillez avoir avec vous (ou me l'envoyer en avance):

* vos données
* votre code R (au minimum capable de charger les données)
* une hypothèse de travail ou question biologique claire

Une consultation statistiques n'implique pas de m'ajouter en tant ue que co-auteur.
Je demande simplement que vous m'ajoutiez au **Remerciements/Acknowledgements** de votre thèse et/ou manuscript.
Je reconnais que dans certains cas, e.g. nombres répétées de consultations sur le même projet incluant le développement de code et analyse spécifique au projet, je peux devenir co-auteur sur un projet.
Cette discussion a habituellement lieu de manière naturelle et à toujours lieu de manière ouverte et ransparente avec les personnes impliquées, étudiant.e.s et PI.s.
Jusqu'à maintenant, je n'ai jamais demandé à être co-auteur, et je suis devenu co-auteur sur 3 articles et j'ai été consulté pour plus de 50 projets.

:::

