---
title: "Biostats uOttawa"
---

{{< include _links.qmd >}}

```{r}
#| label: setup
#| include: FALSE
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
#| fig.align: 'center'
#| out.width: "25%"
dat<-data.frame(a = rnorm(10000))
library(ggplot2)
ggplot(dat, aes(a))+geom_density(color="blue", fill="red") +theme_classic()+xlab("Gaussian distribution")
```

::: {.panel-tabset }


## English

### Biostatistic courses at uOttawa

This regroup the different resources developed for the biostatistic courses at the university of Ottawa
by [Julien Martin](people.qmd)  

#### Applied biostatistics with R (BIO 4X58):

  * BIO4158 english ([course site][4158_course] / [course manual][4158_manual])
  * BIO4558 french ([course site][4558_course] / [course manual][4558_manual])
  * Offered to both undergraduate and graduate students
  * Prerequisite:
    * an introduction class to statisticis is good to have
    * No (or limited) knowledge of R and no (or limited) knowledge of stats expected.


#### Advanced biostatistics and open science (BIO 8940)

  * [course site][8940_course] / [course manual][8940_manual]
  * Bilingual course for graduate students
  * Prerequisite:
    * a functional knowledge of R (loading data, running basic linear models, and making plots) 
    * a good understanding of linear models
    * essentially Bio8940 is a great next steps after completing Bio4x58.

### Extra resources

* An introduction to R
  * english ([course][Rintro] / [course manual][R_way])
  * french ([course][introR] / [course manual][chemin_R])

## Français

### Cours de biostatistique à uOttawa

Le site regroupe les différentes ressources développées par [Julien Martin](people.qmd) pour les cours de biostatistiques à uOttawa

#### Biostatistiques appliquées avec R (BIO 4X58)

  * BIO4158 anglais ([cours][4158_course] / [manuel][4158_manual])
  * BIO4558 français ([cours][4558_course] / [manuel][4558_manual])
  * Cours offerts aux étudiant au baccaulauréat et aux étudiants gradués
  * Pré-requis:
    * cours d'introduction au statistiques recommandée
    * Aucune connaissance de R et des statistiques requises

#### Biostatistiques avancées et science ouverte (BIO8940)

  * [cours][8940_course] / [manuel][8940_manual]
  * Cours bilingues offerts aux étudiants gradués
  * Pré-requis:
    * connaissances fonctionelle de R (chargement de données, graphique et statistiques de bases)
    * bonne compréhension des modèles linéaires
    * Essentiellement Bio4x58

### Tutoriels

* Introduction à R
  * anglais ([cours][Rintro] / [manuel][R_way])
  * français ([cours][introR] / [manuel][chemin_R])


:::

