---
title: "Biostats uOttawa"
---

{{< include _links.qmd >}}

```{r}
#| label: setup
#| include: FALSE
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
#| fig.align: 'center'
#| out.width: "25%"
dat<-data.frame(a = rnorm(10000))
library(ggplot2)
ggplot(dat, aes(a))+geom_density(color="blue", fill="red") +theme_classic()+xlab("Gaussian distribution")
```

::: {.panel-tabset }


## English

### Biostatistic resources for uOttawa students


This regroup the different resources developed for the biostatistic courses at the university of Ottawa
by [Julien Martin](people.qmd)  


#### Courses at uOttawa

* BIO 4X58: Biostatistics with R
  * english BIO4158 ([course site][4158_course] / [course manual][4158_manual])
  * french BIO4558 ([course site][4558_course] / [course manual][4558_manual])

* BIO8940: Advanced biostatistics and open science ([course site][8940_course] / [course manual][8940_manual])

#### Extra resources

* An introduction to R
  * english ([course][Rintro] / [course manual][R_way])
  * french ([course][introR] / [course manual][chemin_R])

## Français

### Resources de biostatistique pour les étudiants de uOttawa

Le site regroupe les différentes ressources développées par [Julien Martin][lab_website] pour les cours de biostatistiques à uOttawa


#### Cours

* BIO 4X58: Biostatistiques avec R
  * anglais BIO4158 ([cours][4158_course] / [manuel][4158_manual])
  * français BIO4558 ([cours][4558_course] / [manuel][4558_manual])

* BIO8940: Advanced biostatistics and open science ([cours][8940_course] / [manuel][8940_manual])

#### Extra resources

* An introduction to R
  * anglais ([cours][Rintro] / [manuel][R_way])
  * français ([cours][introR] / [manuel][chemin_R])


:::

