---
title: "On the R-way to hell"
format:
  html:
    toc: false
---

{{< include _links.qmd >}}

```{r}
#| label: setup
#| include: FALSE
library(yaml)
library(stringr)
library(tibble)
library(dplyr)
library(purrr)
library(glue)
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)
```

## Slides

A few presentations to take as an easy intro to R.

```{r}
schedule_df <- data.frame(
  topic = c("Introduction R", "Data in R", "Simple stats in R"),
  weekno = 1:3
) %>%
  mutate(
    lecture = file.exists(sprintf("slides_r/lec_en-%.2d.qmd", weekno)),
  ) %>%
  mutate(
    slides = case_when(lecture == TRUE ~
      glue("<a class='fa fa-display' href='slides_r/{sprintf(\"lec_en-%.2d.slides.html\", weekno)}' target='_blank'></a> / <a class='fa fa-note-sticky' href='slides_r/{sprintf(\"lec_en-%.2d.notes.html\", weekno)}' target='_blank'></a>"),
      .default = NA),
    topic = ifelse(is.na(topic), "", topic)
  ) %>%
  select(topic, slides)

schedule_df %>%
  kable(
    escape = FALSE, align = c("c", "c"),
    col.names = c(
      "Topic", "Slides"
    ),
    format = "html"
  ) %>%
  kable_styling(
    bootstrap_options = "striped",
    fixed_thead = T
  )
```

## Manual

Here is a link to the the introduction to R manual: [On the R-way to hell][R_way] {{< fa thumbs-up >}} 


## About slides {{< fa display >}} and notes {{< fa note-sticky >}}

### Slides {{< fa display >}} 

Slides in `revealjs` format (html). If you want then as a pdf (*note you might loose some functionality or contents due to tabs and scroll sections*):

1. Open the slides in your browser from a link on this page
2. Press `e` to get into the PDF export mode (*`?print-pdf` should appear near the end of the url and white borders should appear*)
1. Open the in-browser print dialog (CTRL/CMD+P).
1. Change the `Destination` setting to `Save as PDF`.
1. Change the `Layout` to `Landscape`.
1. Change the `Margins` to `None`.
1. Enable the Background graphics option (if you want it)
1. Click Save 🎉

### Notes {{< fa note-sticky >}}

Content of the slides in html format as a self-contained downloadable file and including tabs and scroll sections. 

More importantly, notes have the commenting and annotateing tools activated via <https://hypothes.is/>. If you create a free account , you can annotate and comment slides as well as share your annotations/comments with the public or via private or public groups.
